### 2023-02-08 index.qmd
Initialize Quarto book

---
title             : "Gender differences in infant mental rotation"
shorttitle        : "Infant mental rotation"

author:
  - name          : "Alexander Enge"
    affiliation   : "1,2"
    corresponding : "yes"
    address       : "Stephanstraße 1a, 04103 Leipzig, Germany"
    email         : "enge@cbs.mpg.de"
  - name          : "Shreya Kapoor"
    affiliation   : "1"
  - name          : "Anne-Sophie Kieslinger"
    affiliation   : "1"
  - name          : "Michael A. Skeide"
    affiliation   : "1"
affiliation:
  - id            : "1"
    institution   : "Research Group Learning in Early Childhood, Max Planck Institute for Human Cognitive and Brain Sciences, Leipzig, Germany"
  - id            : "2"
    institution   : "Department of Psychology, Humboldt-Universität zu Berlin"

authornote: |
  \addORCIDlink{Alexander Enge}{0000-0003-0100-2297}

  \addORCIDlink{Shreya Kapoor}{0000-0003-2619-8257}

  \addORCIDlink{Anne-Sophie Kieslinger}{0000-0001-9240-4077}

  The data and code necessary to reproduce the analyses presented here are available at [https://osf.io/k3wdg/?view_only=e3b345f00ee84d318a9990689a1c5a9e](https://osf.io/k3wdg/?view_only=e3b345f00ee84d318a9990689a1c5a9e).

@@

bibliography      : "manuscript_files/references.bib"
csl               : "manuscript_files/apa.csl"

appendix          : "supplement.Rmd"

floatsintext      : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

documentclass     : "apa7"
classoption       : "man,donotrepeattitle"
fontsize          : "10pt"
output            : "papaja::apa6_pdf"

header-includes:
  - \geometry{a4paper}
  - \raggedbottom
  - \usepackage[all]{nowidow}
  - \usepackage{lineno}
  - \usepackage{makecell}
  - \usepackage{setspace}
  - \DeclareCaptionTextFormat{tabletext}{\textup{#1}}
  - \captionsetup[table]{belowskip=20pt,labelfont=bf,labelsep=period,textfont=bf,textformat=tabletext}
  - \captionsetup[figure]{belowskip=10pt,font=small,labelfont=bf,labelsep=period,textfont=normalfont}
---

```{r, setup, include=FALSE}
# Load packages
library(papaja)
library(here)
library(readxl)
library(scales)
library(tidyverse)
library(furrr)
library(metafor)
library(brms)
library(tidybayes)
library(cowplot)

# Load custom helper functions
source(here("manuscript_files", "helper_functions.R"))

# Re-run steps that take a long time?
run <- list(
  bayesian_models = FALSE,
  jackknife_analysis = FALSE,
  sensitivity_analysis = FALSE
)

# Global chunk options
knitr::opts_chunk$set(
  include = FALSE,
  message = FALSE,
  fig.align = "center",
  fig.height = 10,
  fig.pos = "tp",
  fig.width = 7.5,
  out.width = "100%",
  warning = FALSE
)

# Options for MCMC sampling when fitting Bayesian multilevel models
n_iter <- 20000 # Posterior samples per chain, including `n_warmup`
n_warmup <- 2000 # Warmup samples per chain
n_chains <- 4 # Number of (parallel) chains
seed <- 1234 # Random seed to make the results reproducible

# Directory paths
data_dir <- here("data")
models_dir <- here("results/models")
figures_dir <- here("results/figures")
tables_dir <- here("results/tables")

# Read the relevant spreadsheets
raw_screen <- read_tsv(here(data_dir, "02_screen.tsv"), na = "NA")
raw_meta <- read_tsv(here(data_dir, "03_meta.tsv"), na = "NA")
raw_gender <- read_tsv(here(data_dir, "04_gender.tsv"), na = "NA")

# Add columns to the table of experiments for the meta-analysis
raw_meta %>%
  mutate(

    # Add unique experiment identifier
    experiment = str_c(year, article, group, sep = ", "),

    # Add difference between condition means
    mean_diff = case_when(
      !is.na(mean_diff) ~ mean_diff,
      TRUE ~ mean_novel - mean_familiar
    ),
    # Add d_z from paired-samples t-test of condition means (Rosenthal, 1991)
    d_z_t = t / sqrt(sample_size),
    # Add d_z from ANOVA F statistic via conversion to a t statistic
    d_z_f = sqrt(f) / sqrt(sample_size) * sign_f,
    # Add d_z from mean and standard deviation of the difference
    d_z_diff = mean_diff / sd_diff,
    # Add d_av from mean difference and standard deviations
    # See http://dx.doi.org/10.20982/tqmp.14.4.p242
    sd_av = sqrt((sd_novel^2 + sd_familiar^2) / 2),
    d_av = mean_diff / sd_av,
    # Add d from one-sample t-test of novelty preference scores
    d_nov_pref = (nov_pref - 0.5) / sd_nov_pref,

    # Choose one type of outcome variable for each experiment
    di = case_when(
      # 1. If d was reported directed
      !is.na(d) ~ d,
      # 2. If a paired-samples t-test was reported
      !is.na(d_z_t) ~ d_z_t,
      # 3. If an ANOVA was reported
      !is.na(d_z_f) ~ d_z_f,
      # 4. If the difference between means and its SD were reported
      !is.na(d_z_diff) ~ d_z_diff,
      # 5. If the individual condition means and their SDs were reported
      !is.na(d_av) ~ d_av,
      # 6. If a novelty preference score and its SD were reported
      !is.na(d_nov_pref) ~ d_nov_pref
    ),
    # Keep track which type of outcome measure was chosen for each article
    di_type = case_when(
      !is.na(d) ~ "d",
      !is.na(d_z_t) ~ "d_z_t",
      !is.na(d_z_f) ~ "d_z_f",
      !is.na(d_z_diff) ~ "d_z_diff",
      !is.na(d_av) ~ "d_av",
      !is.na(d_nov_pref) ~ "d_nov_pref",
      TRUE ~ "none"
    ) %>%
      factor(levels = c(
        "d", "d_z_t", "d_z_f", "d_z_diff", "d_av", "d_nov_pref", "none"
      )),

    # Apply small sample correction using Hedges' exact method
    # See http://dx.doi.org/10.20982/tqmp.14.4.p242
    dfi = 2 * (sample_size - 1),
    ji = exp(lgamma(dfi / 2) - log(sqrt(dfi / 2)) - lgamma((dfi - 1) / 2)),
    gi = di * ji,

    # Recode gender as a categorical (factor) variable for meta-regression
    gender = case_when(
      female_percent == 1.0 ~ "Female",
      female_percent == 0.0 ~ "Male",
      TRUE ~ "Mixed"
    ) %>% factor(levels = c("Mixed", "Female", "Male")),

    # Recode mean sample age in years (mean-centered) for meta-regression
    age = age_mean / 365.25,
    age_c = age - mean(age, na.rm = TRUE),

    # Recode task type as a categorical (factor) variable for meta-regression
    task = factor(task, levels = c("Habituation", "VoE")),

    # Combine gender and task into one column for plotting
    gender_task = factor(
      str_c(gender, task, sep = ", "),
      levels = c(
        "Female, Habituation",
        "Male, Habituation",
        "Mixed, Habituation",
        "Mixed, VoE"
      )
    )
  ) %>%
  # Order rows by experiment ID
  arrange(experiment) -> dat_all

# Get an overview of the different effect sizes
dat_all %>%
  select(
    article,
    group,
    gender_split,
    gi,
    di,
    di_type,
    d,
    d_z_t,
    d_z_f,
    d_z_diff,
    d_av,
    d_nov_pref
  ) %>%
  print(n = Inf)

# Compute standard errors of the effect sizes based on assumed correlation
# See Hedges' formula on p. 253 in http://dx.doi.org/10.20982/tqmp.14.4.p242
# You'll find a sensitivity analysis for `r_assumed` in the `supplement.Rmd`
r_assumed <- 0.5
dat_all %>%
  mutate(
    ni = sample_size,
    vi = (dfi / (dfi - 2)) * ((2 * (1 - r_assumed)) / ni) *
      (1 + gi^2 * (ni / (2 * (1 - r_assumed)))) - (gi^2 / ji^2),
    sei = sqrt(vi)
  ) %>%
  filter(!is.na(gi)) -> dat_meta_all

# Show number of experiments per gender grouping strategy (mixed/split)
table(dat_meta_all$gender_split)

# Extract either split or mixed experiments only
dat_split <- filter(dat_meta_all, gender_split %in% c("split", "split_only"))
dat_mixed <- filter(dat_meta_all, gender_split %in% c("mixed", "mixed_only"))

# Combine both strategies but preferring mixed experiments
dat_both_mixed <- filter(
  dat_meta_all, gender_split %in% c("mixed", "mixed_only", "split_only")
)

# Combine both strategies but preferring split experiments
dat_both_split <- filter(
  dat_meta_all, gender_split %in% c("split", "mixed_only", "split_only")
)

# We go ahead with the last solution (i.e., prefer split experiments) as to use
# the maximum amount of information while not biasing the gender results
dat_meta <- dat_both_split

# Extract some descriptive statistics so we can paste them in the main text
descriptives <- list(
  n_articles = length(unique(dat_meta$article)),
  n_experiments = nrow(dat_meta),
  n_infants = sum(dat_meta$sample_size),
  percent_female = mean(dat_meta$female_percent, na.rm = TRUE),
  min_age_months = as.integer(min(dat_meta$age_min, na.rm = TRUE) / 30.417),
  max_age_months = as.integer(max(dat_meta$age_max, na.rm = TRUE) / 30.417),
  mean_age_weighted = print_days_months(
    sum(dat_meta$age_mean * dat_meta$ni) / (sum(dat_meta$ni)),
    long = TRUE
  ),
  n_experiments_habituation = nrow(filter(dat_meta, task == "Habituation")),
  n_experiments_voe = nrow(filter(dat_meta, task == "VoE"))
)
```

\setcounter{page}{1}
\resetlinenumber

# Gender differences in infant mental rotation

\bigskip

# Research highlights

* We analyzed effect sizes of `r descriptives$n_experiments` mental rotation experiments including `r formatC(descriptives$n_infants, big.mark = ",")` infants

* Looking time reveals that 3–16-months-old infants are able to perform mental rotation

* Mental rotation is more reliable in male infants compared to female infants

# Abstract

Mental rotation, the cognitive process of moving an object in mind to predict how it looks in a new orientation, is tightly coupled to intelligence, learning, and educational achievement [@shepard1971; @hegarty1999; @johnson2005]. On average, males solve mental rotation tasks slightly faster than females [@linn1985; @voyer1995; @voyer2011; @maeda2013]. When such behavioral differences emerge during development, however, remains poorly understood [@lauer2019a]. Here we analyzed effect sizes derived from `r descriptives$n_experiments` experiments conducted in `r formatC(descriptives$n_infants, big.mark = ",")` infants aged 3--16 months. We robustly found that male infants recognized rotated objects more reliably than female infants. These findings indicate that gender differences in mental rotation are already present in the first months of life.

*Keywords*: mental rotation; spatial cognition; spatial ability; infants; gender; meta-analysis

\newpage

# Introduction

The cognitive ability to move visual object representations in mind for recognition across different orientations, known as mental rotation, emerges in the first three months of life [@moore2020; @johnson2020]. Mental rotation is a key component of intelligence and a powerful predictor of learning outcome and educational achievement [@shepard1971; @hegarty1999; @johnson2005].

Previous meta-analyses revealed that males solve mental rotation tasks slightly faster than females on average [@linn1985; @voyer1995; @voyer2011; @maeda2013]. Effect sizes of this difference, however, are heterogeneous and often only medium in size (mean weighted $g = 0.37\text{--}0.73$). Interestingly, a recent meta-analysis in 3--17-year-old children and adolescents suggests only a small-to-medium difference [mean weighted $g = 0.39$\; @lauer2019a]. Whether gender differences in mental rotation behavior already emerge during infancy remains unknown.

In the present study, we meta-analyzed `r descriptives$n_experiments` effect sizes derived from looking times in mental rotation tasks performed by `r formatC(descriptives$n_infants, big.mark = ",")` infants (`r print_perc(descriptives$percent_female)` female) aged `r descriptives$min_age_months` to `r descriptives$max_age_months` months (mean age of `r descriptives$mean_age_weighted`\; Supplementary Table\ \@ref(tab:tabs1)) [@rochat1996; @hespos1997; @moore2008; @quinn2008; @moore2011; @frick2013b; @mohring2013; @schwarzer2013; @schwarzer2013a; @frick2014b; @quinn2014; @lauer2015; @antrilli2016; @christodoulou2016; @constantinescu2018; @erdmann2018; @gerhard2018; @slone2018; @kaaz2020; @gerhard-samunda2021; @kelch2021]. All tasks were embedded either into habituation experiments (`r descriptives$n_experiments_habituation` experiments) or violation of expectation experiments (`r descriptives$n_experiments_voe` experiments) [@fantz1964; @baillargeon1985]. These experiments comprised real world stimuli [e.g., toy objects\; @antrilli2016], three-dimensional digital stimuli [e.g., cube figures\; @moore2008], or two-dimensional digital stimuli [e.g., digits\; @quinn2008]. In habituation experiments, infants repeatedly saw an object until their looking times declined before they were presented with a mirror image of the object or with the familiar object at a new angle. Longer looking times at the mirror image were taken as evidence that an infant still recognized the familiar object after rotation through the new orientation. In violation of expectation experiments, infants were habituated to an object that was revolving repeatedly through a certain angle. Then, either the familiar object or an unseen object was shown while they were revolving through a certain angle. Subsequently, the object disappeared behind an occluder. Finally, the occluder was removed and either the object or its mirror object were shown. Larger differences in looking times for the familiar object versus the unseen mirror image (at the new angle) were taken as evidence that an infant still recognized the familiar object after rotation through the new angle. In contrast, looking times for both objects were expected to be similar if an infant did not recognize the familiar object from the new angle.

Following previous work in older populations, we hypothesized that looking time differences in mental rotation experiments are on average longer in male compared to female infants. Effect sizes were assumed to be small.

```{r, meta}
# Specify priors
prior_meta <- c(
  set_prior("normal(0, 1)", class = "b"),
  set_prior("cauchy(0, 0.3)", class = "sd")
)

# Run prior predictive simulation
dir.create(models_dir, showWarnings = FALSE, recursive = TRUE)
brms_file_refit <- ifelse(run$bayesian_models, "always", "never")
res_prior_meta <- brm(
  gi | se(sei) ~ 0 + Intercept + (1 | article / experiment),
  data = dat_meta,
  prior = prior_meta,
  sample_prior = "only",
  save_pars = save_pars(all = TRUE),
  chains = n_chains,
  iter = n_iter,
  warmup = n_warmup,
  cores = n_chains,
  control = list(adapt_delta = 0.99),
  seed = seed,
  file = here(models_dir, "res_prior_meta"),
  file_refit = brms_file_refit
)
summary(res_prior_meta)

# Run Bayesian multilevel model
res_meta <- update(
  res_prior_meta,
  sample_prior = FALSE,
  seed = seed,
  file = here(models_dir, "res_meta"),
  file_refit = brms_file_refit
)
summary(res_meta)

# Get posterior probability mass > 0 for the meta-analytic effect
(hyp_meta <- hypothesis(res_meta, "Intercept > 0")$hypothesis)

# Extract posterior draws for the meta-analytic effects
spread_draws(res_meta, `b_.*`, `sd_.*`, regex = TRUE, ndraws = NULL) %>%
  # Compute variances and ICC from standard deviations
  mutate(
    intercept = b_Intercept,
    sigma_article = sd_article__Intercept,
    sigma_experiment = `sd_article:experiment__Intercept`,
    sigma2_article = sigma_article^2,
    sigma2_experiment = sigma_experiment^2,
    sigma2_total = sigma2_article + sigma2_experiment,
    icc = sigma2_article / sigma2_total,
    .keep = "unused"
  ) -> draws_meta

# Summarize as means and 95% credible intervals
(summ_meta <- as.list(mean_qi(draws_meta)))
```

```{r, fig1, include=TRUE, fig.height=14, fig.width=12, fig.cap="(ref:fig1-caption)"}
# Get posterior draws for the effect *in each experiment*
epred_draws_meta <- epred_draws(res_meta, dat_meta, ndraws = NULL) %>%
  mutate(experiment_f = factor(experiment))

# Create forest plot
dat_meta %>%
  # Make sure the plot will be ordered alphabetically by experiment IDs
  arrange(experiment) %>%
  mutate(
    experiment_f = fct_rev(fct_expand(factor(experiment), "model")),
    # Show article labels only for the first experiment (row) per article
    article = if_else(article == lag(article, default = ""), "", article),
    # Compute frequentist confidence intervals for each experiment
    ci_lb = gi - qnorm(0.05 / 2, lower.tail = FALSE) * sqrt(vi),
    ci_ub = gi + qnorm(0.05 / 2, lower.tail = FALSE) * sqrt(vi),
    ci_print = print_mean_ci(gi, ci_lb, ci_ub)
  ) %>%
  # Prepare plotting canvas
  ggplot(aes(x = gi, y = experiment_f)) +
  geom_vline(xintercept = seq(-3, 3, 0.5), color = "grey90") +
  # Add article and group labels as text on the left
  geom_text(aes(x = -9.9, label = article), hjust = 0) +
  geom_text(aes(x = -7.1, label = group), hjust = 0) +
  # Add experiment-specific effect sizes and CIs as text on the right
  geom_text(aes(x = 3.7, label = print_num(gi)), hjust = 1) +
  geom_text(aes(x = 4.4, label = print_num(ci_lb)), hjust = 1) +
  geom_text(aes(x = 5.1, label = print_num(ci_ub)), hjust = 1) +
  # Add Bayesian credible intervals for each experiment
  stat_interval(
    aes(x = .epred),
    data = epred_draws_meta,
    alpha = .8,
    point_interval = "mean_qi",
    .width = c(0.5, 0.95),
  ) +
  scale_color_grey(
    start = 0.85, end = 0.65,
    labels = as_mapper(~ scales::percent(as.numeric(.x)))
  ) +
  # Add experiment-specific effect sizes and CIs as dots with error bars
  geom_linerange(aes(xmin = ci_lb, xmax = ci_ub), size = 0.35) +
  geom_point(aes(size = ni), shape = 22, fill = "white") + # Or (1 / vi)?
  # Add posterior distribution for the meta-analytic effect
  stat_halfeye(
    aes(x = intercept, y = -1),
    draws_meta,
    point_interval = "mean_qi",
    .width = c(0.95)
  ) +
  annotate(
    "text",
    x = c(-9.9, 3.7, 4.4, 5.1),
    y = -0.5,
    label = c(
      "Three-level model",
      print_num(summ_meta$intercept),
      print_num(summ_meta$intercept.lower),
      print_num(summ_meta$intercept.upper)
    ),
    hjust = c(0, 1, 1, 1),
    fontface = "bold"
  ) +
  # Add column headers
  annotate(
    "rect",
    xmin = -Inf,
    xmax = Inf,
    ymin = descriptives$n_experiments + 0.5,
    ymax = Inf,
    fill = "white"
  ) +
  annotate(
    "text",
    x = c(-9.9, -7.1, 0, 3.7, 4.4, 5.1),
    y = descriptives$n_experiments + 1.5,
    label = c(
      "Article",
      "Experiment",
      "Effect size plot",
      "Effect size",
      "2.5%",
      "97.5%"
    ),
    hjust = c(0, 0, 0.5, 1, 1, 1),
    fontface = "bold"
  ) +
  # Styling
  coord_cartesian(
    ylim = c(-1.5, descriptives$n_experiments + 2), expand = FALSE, clip = "off"
  ) +
  scale_x_continuous(breaks = seq(-3, 3, 0.5)) +
  annotate("segment", x = -3.3, xend = 3.3, y = -1.5, yend = -1.5) +
  labs(
    x = expression("Hedges'" ~ italic("g")),
    size = "Sample size",
    color = "CrI level"
  ) +
  theme_minimal() +
  theme(
    legend.position = "bottom",
    axis.text.x = element_text(family = "Helvetica", color = "black"),
    axis.text.y = element_blank(),
    axis.ticks.x = element_line(colour = "black"),
    axis.title.x = element_text(hjust = 0.67, margin = margin(b = -15)),
    axis.title.y = element_blank(),
    panel.grid = element_blank(),
    text = element_text(family = "Helvetica")
  )

# Save the plot
dir.create(figures_dir, showWarnings = FALSE)
ggsave(here(figures_dir, "fig1_meta.pdf"), width = 12, height = 14)
```

(ref:fig1-caption) **Mental rotation performance.** A Bayesian three-level meta-analysis provided evidence for mental rotation ability in infants. White squares depict the effect sizes (Hedges' $g$) for infants' mental rotation performance in all individual experiments and black lines depict their 95% confidence intervals. Gray bars indicate the 50% and 95% credible intervals (CrI) from the Bayesian model, which take into account that experiments with smaller sample sizes or more extreme effect sizes provide less reliable information. The last line shows the meta-analytic effect size (black dot) together with its 95% CrI (black line) and its posterior distribution (gray curve).

# Results

## Mental rotation performance

For our first meta-analytic model, effect sizes were quantified as the standardized mean difference in infants' looking times for novel and familiar rotated objects. Using this effect size index, we ran a Bayesian three-level random-effects model to test if there was evidence that infants did perform mental rotation. Across studies, infants indeed looked longer at novel rotated objects than at familiar rotated objects, with a standardized mean difference of $g = `r summ_meta$intercept`$, 95% credible interval (CrI) [`r summ_meta$intercept.lower`, `r summ_meta$intercept.upper`] (Figure\ \@ref(fig:fig1)). The probability for this effect being greater than zero was `r print_prob(hyp_meta$Post.Prob)`. The heterogeneity of effect sizes was $\sigma_{\text{experiment}}^2 = `r summ_meta$sigma2_experiment`$, 95% CrI [`r summ_meta$sigma2_experiment.lower`, `r summ_meta$sigma2_experiment.upper`], at the experiment level and $\sigma_{\text{article}}^2 = `r summ_meta$sigma2_article`$, 95% CrI [`r summ_meta$sigma2_article.lower`, `r summ_meta$sigma2_article.upper`] at the article level. Therefore, `r print_perc(1 - summ_meta$icc)` of the heterogeneity between effect sizes was attributable to differences between experiments *within* articles and `r print_perc(summ_meta$icc)` was attributable to differences *between* articles.

## Effects of gender, age, and task type

```{r, reg}
# Set numerical contrasts for factor variables
contrasts(dat_meta$gender) <- MASS::contr.sdif(3)
contrasts(dat_meta$task) <- MASS::contr.sdif(2)

# Specify priors
prior_reg <- c(
  set_prior("normal(0, 1)", class = "b", coef = "Intercept"),
  set_prior("normal(0, 0.5)", class = "b"),
  set_prior("cauchy(0, 0.3)", class = "sd")
)

# Run prior predictive simulation
res_prior_reg <- brm(
  gi | se(sei) ~ 0 + Intercept + gender * age_c + task +
    (1 | article / experiment),
  data = dat_meta,
  prior = prior_reg,
  sample_prior = "only",
  save_pars = save_pars(all = TRUE),
  chains = n_chains,
  iter = n_iter,
  warmup = n_warmup,
  cores = n_chains,
  control = list(adapt_delta = 0.99),
  seed = seed,
  file = here(models_dir, "res_prior_reg"),
  file_refit = brms_file_refit
)
summary(res_prior_reg)

# Run Bayesian multilevel model
res_reg <- update(
  res_prior_reg,
  sample_prior = FALSE,
  seed = seed,
  file = here(models_dir, "res_reg"),
  file_refit = brms_file_refit
)
summary(res_reg)

# Get posterior probability mass > 0 for all regression weights
(hyps_brm_reg <- list(
  intercept = hypothesis(res_reg, "Intercept > 0")$hypothesis,
  female_mixed = hypothesis(res_reg, "gender2M1 < 0")$hypothesis,
  male_female = hypothesis(res_reg, "gender3M2 > 0")$hypothesis,
  age = hypothesis(res_reg, "age_c > 0")$hypothesis,
  voe_habituation = hypothesis(res_reg, "task2M1 > 0")$hypothesis,
  female_mixed_age = hypothesis(res_reg, "gender2M1:age_c > 0")$hypothesis,
  male_female_age = hypothesis(res_reg, "gender3M2:age_c > 0")$hypothesis
))

# Extract posterior draws for the meta-analytic effects
spread_draws(res_reg, `b_.*`, `sd_.*`, regex = TRUE, ndraws = NULL) %>%
  # Compute variances and ICC from standard deviations
  mutate(
    intercept = b_Intercept,
    female_mixed = b_gender2M1,
    male_female = b_gender3M2,
    age = b_age_c,
    voe_habituation = b_task2M1,
    female_mixed_age = `b_gender2M1:age_c`,
    male_female_age = `b_gender3M2:age_c`,
    sigma_article = sd_article__Intercept,
    sigma_experiment = `sd_article:experiment__Intercept`,
    sigma2_article = sd_article__Intercept^2,
    sigma2_experiment = `sd_article:experiment__Intercept`^2,
    sigma2_total = sigma2_article + sigma2_experiment,
    icc = sigma2_article / sigma2_total,
  ) -> draws_reg

# Summarize as means and 95% credible intervals
(summ_reg <- as.list(mean_qi(draws_reg)))
```

As a next step, we conducted a meta-regression analysis to test if the gender of the infants, their age, or the type of mental rotation task was related to mental rotation performance (Figure\ \@ref(fig:fig2)). Indeed, experiments with all-male samples revealed larger looking time differences than experiments with all-female samples, $b = `r summ_reg$male_female`$ (where $b = \Delta{g}$), 95% CrI [`r summ_reg$male_female.lower`, `r summ_reg$male_female.upper`]. The probability for this effect being larger than zero was `r print_prob(hyps_brm_reg$male_female$Post.Prob)`. We found no difference between all-female and mixed-gender samples, $b = `r summ_reg$female_mixed`$, 95% CrI [`r summ_reg$female_mixed.lower`, `r summ_reg$female_mixed.upper`] (`r print_prob(hyps_brm_reg$female_mixed$Post.Prob)` probability of an effect larger than zero). Additionally, mean age was not related to mental rotation performance, with a change per year of $b = `r summ_reg$age`$, 95% CrI [`r summ_reg$age.lower`, `r summ_reg$age.upper`]. We also did not detect an interaction between gender and age ([females - mixed] $\times$ age: $b = `r summ_reg$female_mixed_age`$, 95% CrI [`r summ_reg$female_mixed_age.lower`, `r summ_reg$female_mixed_age.upper`]; [males - females] $\times$ age: $b = `r summ_reg$male_female_age`$, 95% CrI [`r summ_reg$male_female_age.lower`, `r summ_reg$male_female_age.upper`]). Finally, there was weak evidence that violation of expectation tasks yielded larger effects than habituation tasks, $b = `r summ_reg$voe_habituation`$, 95% CrI [`r summ_reg$voe_habituation.lower`, `r summ_reg$voe_habituation.upper`]. The probability for this effect being greater than zero was `r print_prob(hyps_brm_reg$voe_habituation$Post.Prob)`.

```{r, fig2, include=TRUE, fig.height=5, fig.width=12, fig.cap="(ref:fig2-caption)"}
# Get draws from the posterior distribution *for each experiment*
epred_draws_reg <- epred_draws(
  res_reg,
  dat_meta,
  ndraws = NULL,
  re_formula = NA
)

# Use colors as proposed in https://arxiv.org/abs/2107.02270
# The four colors code for a combination of tasks (Habituation, VoE) and gender
# (female, male, mixed)
plot_reg_colors <- list(
  habituation = c(
    "Female, Habituation" = "#5790fc",
    "Male, Habituation" = "#f89c20",
    "Mixed, Habituation" = "#e42536"
  ),
  voe = c("Mixed, VoE" = "#964a8b")
)

# Create regression plot
dat_meta %>%
  ggplot(aes(x = age * 12, y = gi)) +
  geom_hline(yintercept = seq(-1, 2, 0.5), color = "grey90") +
  annotate(
    "rect",
    xmin = 5.5, xmax = Inf, ymin = 1.25, ymax = Inf,
    color = NA, fill = "white"
  ) +
  # Regression lines and CrIs for Habituation tasks
  stat_lineribbon(
    aes(y = .epred, color = gender_task),
    data = epred_draws_reg,
    alpha = .4,
    point_interval = "mean_qi",
    .width = c(0.5, 0.95)
  ) +
  # Individual study effect sizes for Habituation tasks
  geom_point(aes(color = gender_task, size = ni), shape = 0) +
  scale_color_manual(
    values = plot_reg_colors$habituation,
    breaks = names(plot_reg_colors$habituation),
    labels = c("Females", "Males", "Mixed gender"),
    na.value = NA
  ) +
  guides(color = guide_legend(
    title = "Habituation tasks",
    override.aes = list(fill = NA),
    order = 1
  )) +
  # Regression lines and CrIs for VoE tasks
  ggnewscale::new_scale_color() +
  stat_lineribbon(
    aes(y = .epred, color = gender_task),
    data = epred_draws_reg,
    fill = NA,
    alpha = .4,
    point_interval = "mean_qi",
    .width = c(0.5, 0.95)
  ) +
  # Individual study effect sizes for VoE tasks
  geom_point(aes(color = gender_task, size = ni), shape = 0) +
  scale_color_manual(
    values = plot_reg_colors$voe,
    breaks = names(plot_reg_colors$voe),
    labels = c("Mixed gender"),
    na.value = NA
  ) +
  guides(color = guide_legend(title = "VoE tasks", order = 2)) +
  # Styling
  coord_cartesian(expand = FALSE) +
  scale_x_continuous(limits = c(2.9, 16.1), breaks = seq(3, 16, 1)) +
  scale_y_continuous(limits = c(-1.2, 2.2), breaks = seq(-1, 2, 0.5)) +
  scale_fill_grey(
    start = 0.85, end = 0.65,
    labels = as_mapper(~ scales::percent(as.numeric(.x)))
  ) +
  labs(
    x = "Age (months)",
    y = expression("Hedges'" ~ italic("g")),
    fill = "CrI level",
    size = "Sample size"
  ) +
  theme_classic() +
  theme(
    axis.text = element_text(family = "Helvetica", color = "black"),
    axis.ticks = element_line(color = "black"),
    legend.direction = "vertical",
    legend.key = element_blank(),
    legend.position = "none",
    panel.grid = element_blank(),
    text = element_text(family = "Helvetica", color = "black")
  ) -> plot_reg

# Extract the legend so that we can put it inside the plot later on
plot_reg_legend <- get_legend(plot_reg + theme(legend.position = "top"))

# Define new labels for the regression coefficients
coef_colnames <- c(
  b_Intercept = expression("Intercept (Hedges'" ~ italic(g) * ")"),
  b_gender2M1 = expression("Females - mixed"),
  b_gender3M2 = expression("Males - females"),
  b_age_c = expression("Age (per year)"),
  b_task2M1 = expression("Habituation - VoE"),
  `b_gender2M1:age_c` = expression("(Females - Mixed)" %*% "age"),
  `b_gender3M2:age_c` = expression("(Males - Females)" %*% "age")
)

# Plot posterior distributions of the regression coefficients
epred_draws_reg_coef <- tidy_draws(res_reg)
epred_draws_reg_coef %>%
  # Convert to long format
  select(all_of(names(coef_colnames))) %>%
  gather() %>%
  mutate(coef = factor(key, levels = names(coef_colnames))) %>%
  # Plot coefficients as "half eyes" (mean + CrIs + distribution)
  ggplot(aes(x = value, y = fct_rev(coef))) +
  geom_vline(xintercept = seq(-1, 1, 0.5), color = "grey90") +
  stat_halfeye(point_interval = "mean_qi", .width = c(0.5, 0.95)) +
  # Styling
  coord_cartesian(xlim = c(-1.25, 1.25), clip = "off") +
  scale_x_continuous(breaks = seq(-1, 1, 0.5)) +
  scale_y_discrete(labels = coef_colnames) +
  labs(x = expression("Regression weight (" * Delta * italic("g") * ")")) +
  annotate(
    "text",
    label = "Fixed effects", x = -3.175, y = 7.86, hjust = 0,
    family = "Helvetica", fontface = "bold", color = "black"
  ) +
  theme_minimal() +
  theme(
    axis.line.x = element_line(colour = "black"),
    axis.text.x = element_text(family = "Helvetica", color = "black"),
    axis.text.y = element_text(
      family = "Helvetica", color = "black", size = 3.88 * .pt,
      hjust = 0, vjust = -0.1, margin = margin(l = 20)
    ),
    axis.ticks.x = element_line(color = "black"),
    axis.ticks.y = element_blank(),
    axis.title.y = element_blank(),
    panel.grid = element_blank(),
    text = element_text(family = "Helvetica", color = "black")
  ) -> plot_coef

# Combine the two regression plots
plot_grid(
  plot_reg, plot_coef,
  nrow = 1, rel_widths = c(3, 2), labels = "AUTO",
  label_size = 11, label_fontfamily = "Helvetica",
  label_x = 0.008, label_y = 0.99
) +
  draw_plot(plot_reg_legend, x = 0.385, y = 0.865, hjust = 0.5, vjust = 0.5)

# Save plot
ggsave(here(figures_dir, "fig2_reg.pdf"), width = 12, height = 5)
```

(ref:fig2-caption) **Effects of gender, age, and task.** (A) Squares show the effect size (Hedges' $g$) for infants' mental rotation performance in each of the `r descriptives$n_experiments` individual experiments. Squares are color-coded according to the type of habituation task and the gender of the infants (blue = habituation task, all-female sample; yellow = habituation task, all-male sample; red = habituation task, mixed-gender sample; purple = violation of expectation [VoE] task, mixed-gender sample). Lines indicate the best-fit regression estimates according to a Bayesian three-level meta-regression model and gray ribbons indicate their corresponding 50% and 95% credible interval (CrI). (B) Fixed effect estimates obtained from the Bayesian three-level meta-regression model are depicted as black dots together with their 50% CrI (thick black lines) and 95% CrI (thin black lines). Gray curves indicate the posterior distribution for each effect.

```{r, gender}
# Compute relevant effect sizes for the meta-analysis of gender differences
raw_gender %>%
  # Remove effect sizes from experiments with redundant samples
  filter(!redundant) %>%
  # Add columns
  mutate(

    # Add unique experiment identifier
    experiment = str_c(year, article, group, sep = ", "),

    # Re-code non-significant F statistics as an effect size of d = 0
    f = as.numeric(f),
    f_assumed = ifelse(is.nan(f), 0, f),

    # Add d from two-samples t-test (Lakens, 2013)
    d_t = t * sqrt(1 / female_n + 1 / male_n),

    # Add d from ANOVA F statistic via conversion to a t statistic
    d_f = sqrt(f_assumed) * sign_f * sqrt(1 / female_n + 1 / male_n),

    # Add d from mean difference and pooled standard deviation
    mean_diff = mean_diff_males_mean - mean_diff_females_mean,
    sd_diff_pooled_numerator = (male_n - 1) * (mean_diff_males_sd^2) +
      (female_n - 1) * (mean_diff_females_sd^2),
    df = male_n + female_n - 2,
    sd_diff_pooled = sqrt(sd_diff_pooled_numerator / df),
    d_diff = mean_diff / sd_diff_pooled,

    # Add d from one-sample t-test of novelty preference scores
    mean_nov_pref = novelty_pref_males_mean - novelty_pref_females_mean,
    sd_nov_pref_pooled_numerator = (male_n - 1) * (novelty_pref_males_sd^2) +
      (female_n) * (novelty_pref_females_sd^2),
    sd_nov_pref_pooled = sqrt(sd_nov_pref_pooled_numerator / df),
    d_nov_pref = mean_nov_pref / sd_nov_pref_pooled,

>>>>

# Welcome {.unnumbered}

This webpage contains the code and results for the following paper:

> Enge, A., Kapoor, S., Kieslinger, A.-S., & Skeide, M. A. (*under review*). A meta-analysis of mental rotation in the first years of life

## Acknowledgments

@@
